### 2023-12-19 conclusions/imag.tex
Few more lines, plus déblocage de moi

The potential chip that would be created has been analyzed, there are also other aspects to take into account. The system being designed to run \acp{NN}, the training of the \ac{NN} also consumes energy

>>>>

The potential chip that would be created has been analyzed, there are also other aspects to take into account. The system being a way to run a wide variety of \acp{NN}, depending on the scale of the project the cip is used in, the impact of training is different. However, the main application being for embedded systems, training the system for a few hours is negligible when the final circuit is used thousands to millions times in its life cycle.
The inference of the \ac{NN} also has an environmental impact due to the power it uses. But the goal of building an analog \ac{NN} is to reduce both execution time and energy consumption, and while the energy comsumption wasn't evaluated in this thesis
